General thermodynamic constraints on magic states for quantum computation

### 2021-04-16 magic_paper.tex
New subsection added. Needs copy-paste of prior eqns but with primes added.

\title{Thermodynamic constraints for magic states in quantum computation}

@@

\section{Magic bounds in arbitrary stabiliser fragments}
\label{sec:stab}

@@

\end{proof}

\subsection{Lower magic bounds via majorisation}
\label{sec:lower_bounds}

>>>>

\title{General thermodynamic constraints on magic states for quantum computation}

@@

\section{Magic bounds in arbitrary stabiliser fragments and energetic costs of distillation}
\label{sec:stab}

@@

\end{proof}
We note that the above bounds are not optimal, and since we only use part of the Lorenz curve they can be improved upon. However, we find numerically that they do better than, for example, the constraint coming from the peak of the curve. Similar bounds can be obtained from the decreasing part of the Lorenz curve, but they do not shed any more light on distillation bounds.

\subsection{Distillation bounds and energy dependencies}
The previous section was focussed on an individual fragment, and while this does shed light on how physical constraints may, or may not, constrain protocols it is a bit indirect. However it is possible to adapt these bounds and put them in a more natural light.

For this we now drop the condition that $\sigma$ is left invariant under the distillation protocol, and assume it transforms to some $\sigma'$. This output state must be some other stabilizer state and so has a positive Wigner function also. The strategy is then to use how any protocol transforms $\sigma$ to act as a measure of physical features, such as energy, of the protocol. Therefore we are interested in the conditions under which $(\rho, \sigma) \rightarrow (\rho', \sigma')$. For this we can use the full definition of relative majorization on the associated Wigner functions, and obtain distillation bounds from
\begin{equation}
(W_\rho(\x), W_\sigma(\x) ) \succ (W_{\rho'}(\x), W_{\sigma'}(\x) ).
\end{equation}
The condition for this that $L_{\rho |\sigma } (x) \ge L_{\rho'|\sigma'} (x)$, and so exactly the same analysis applies as in the previous case, but now with the Gibbs-recaling parameters for the output state being different from the input state \ddd{[cite recent Renes paper]}.

If the physical system has Hamiltonian $H$, and experimentally it can be cooled down to some reference temperature $T$ then we can consider the reference equilibrium state $\sigma = e^{-\beta H}/\Z$, and estimate the energetic and entropic of protocols in terms of how they transform $\sigma$ to some other $\sigma'$. For example, if $\sigma'$ is close to the ground state of the system then we know that a great deal of entropy is dumped by the process. This allows us to parameterise our distillation bounds in more convenient terms.

The state $\sigma'$ will in general not be an equilibrium state, or have any temperature associated to it. However we can still associate thermodynamic variables to it as follows: we consider what changes in Hamiltonian are required in order for the output state $\sigma'$ to still be an equilibrium state at the reference temperature $T$. Therefore $H\rightarrow H'$ such that $\sigma' = e^{-\beta H'}/\Z'$ and so the Lorenz curve of the output state $\rho'$ relative to $\sigma'$ will be expressible in terms of the free energy $F'(\beta) = -\beta^{-1} \log \Z'$ and the spectrum of the Hamiltonian $H'$. We find that \ddd{[Details? Expect that we now get free energy differences $\Delta F := F' - F$ appearing.]}
\subsection{Lower magic bounds via majorisation}
\label{sec:lower_bounds}
